R Notebook

### 2021-08-11 gc_ramp_comparison.Rmd
resolution plates and asymmetry

```{r, include=FALSE}
# Libraries
library(tidyverse) # What are we without the tidyverse? c:
library(plotly)
library(ggrepel)
library(ggsci)
library(ggsignif)

@@

# Make a tibble containing all of the integration data
peak_analysis <- peak_data %>%
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0)

@@

>>>>

```{r, include=FALSE}
# Libraries
library(tidyverse) # What are we without the tidyverse? c:
library(plotly)
library(ggrepel)
library(ggsci)
library(ggsignif)
library(ggdist)

@@

# Make a tibble containing all of the integration data
peak_analysis <- peak_data %>%
  select(-injection_details) %>% 
  unnest(integration_results) %>% 
  filter(nchar(`Peak Name`) > 0) %>% 
  filter(sample != "TCBAME-2") %>% # Don't need this sample
  # Add ramp information
  mutate(ramp = str_extract(sample, "\\d"))

@@

```{r}
p_bame_resolution <- peak_analysis %>% 
  filter(!is.na(`Resolution (EP)`)) %>% 
  ggplot() +
  aes(x = `Resolution (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Resolution Versus Ramp Rate") +
  xlab("Resolution (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_resolution
```

```{r}
p_bame_plates <- peak_analysis %>% 
  filter(!is.na(`Plates (EP)`)) %>% 
  ggplot() +
  aes(x = `Plates (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Plates Versus Ramp Rate") +
  xlab("Plates (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_plates
```

```{r}
p_bame_asymmetry <- peak_analysis %>% 
  filter(!is.na(`Asymmetry (EP)`)) %>% 
  ggplot() +
  aes(x = `Asymmetry (EP)`, y = ramp) +
  stat_slab(aes(color = ramp,
                fill = ramp), 
            height = 0.5) +
   geom_point(aes(color = ramp, y = as.numeric(ramp) - 0.15),
             size = 2, 
             alpha = 0.3) +
  stat_pointinterval() +
  ggtitle("DB5-HT 30m Asymmetry Versus Ramp Rate") +
  xlab("Asymmetry (EP)") +
  ylab("Ramp Rate (C per min)") +
  scale_color_npg() +
  scale_fill_npg() +
  theme_minimal()
p_bame_asymmetry
```

## Save Images
```{r}
ggsave("fig_output/p_bame_overview.png", p_bame_overview)
```
